V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298~Tau~e

### 2022-01-03 src/ms.tex
rm lineno
pesky }

\documentclass[linenumbers,twocolumn]{aastex631}

@@

%%%%%%%%%%%%%%%%%%%%
% abstract must be < 250 words
% currently at 180 words
%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

@@

Through an intensive radial velocity campaign, \cite{suarez21} presented a new mass detection for \planetb and \planete. Our updated radius estimate for \planetb in combination with the mass estimate provided by \cite{suarez21} would yield a density of $1.29$~g/cm\textsuperscript{3}, which is slightly higher than what was originally reported. Our updated radius for \planete would yield a lower density of $2.04$~g/cm\textsuperscript{3}, which is still within a 1-$\sigma$ agreement with \cite{suarez21}. However, the period estimate for \planete is at a 4-$\sigma$ disagreement for the period estimate provided in this study and at a 2-$\sigma$ disagreement with the minimum period constraint provided by this new \tess\ data.}

>>>>

\documentclass[twocolumn]{aastex631}

@@

\begin{abstract}

@@

Through an intensive radial velocity campaign, \cite{suarez21} presented a new mass detection for \planetb and \planete. Our updated radius estimate for \planetb in combination with the mass estimate provided by \cite{suarez21} would yield a density of $1.29$~g/cm\textsuperscript{3}, which is slightly higher than what was originally reported. Our updated radius for \planete would yield a lower density of $2.04$~g/cm\textsuperscript{3}, which is still within a 1-$\sigma$ agreement with \cite{suarez21}. However, the period estimate for \planete is at a 4-$\sigma$ disagreement for the period estimate provided in this study and at a 2-$\sigma$ disagreement with the minimum period constraint provided by this new \tess\ data.
